### 2016-02-27 ms.tex
initial

\documentclass{emulateapj}

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}

\newcommand{\IRAS}{{\it IRAS}}
\newcommand{\HERSCHEL}{{\it Herschel}}
\newcommand{\SPITZER}{{\it Spitzer}}
\newcommand{\WISE}{{\it WISE}}

\bibpunct{(}{)}{;}{a}{}{,}

\shorttitle{WISE/NEOWISER Coadds}

\shortauthors{Meisner et al.}

\begin{document} 
\title{Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images}

\author{Aaron M. Meisner\altaffilmark{1,2}}
\author{Dustin Lang\altaffilmark{3}}
\author{David J. Schlegel\altaffilmark{2}}

\altaffiltext{1}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, USA}
\altaffiltext{2}{Lawrence Berkeley National Laboratory, Berkeley, CA, 94720, USA}
\altaffiltext{3}{Department of Astronomy \& Astrophysics and Dunlap Institute, University of Toronto, Toronto, ON M5S 3H4, Canada}

\begin{abstract} 
Thanks to the Wide-field Infrared Survey Explorer (WISE) mission's
NEOWISE-Reactivation (NEOWISER) program, an entire year of post-reactivation W1
and W2 exposures were made publicly available in 2015. This data set consists of
$\sim$2.5 million exposures in each band, effectively doubling the amount
of WISE imaging available at 3.4$\mu$m and 4.6$\mu$m relative to the AllWISE
release. We have created the first ever full-sky set of coadds combining all 
publicly available W1 and W2 exposures from both the AllWISE and 
NEOWISER mission phases. We employ an adaptation of the unWISE image coaddition
framework \citep{lang14}, which preserves the native WISE angular resolution 
and is optimized for forced photometry. By incorporating two additional scans
of the entire sky, we not only improve the W1/W2 depths, but also largely
eliminate time-dependent artifacts such as off-axis moonlight contamination.
We anticipate that our new coadds will have a broad range of 
applications, including target selection for upcoming spectroscopic cosmology 
surveys, discovery of massive galaxy clusters at high redshift, and 
identification of high-redshift quasars. In particular, our full-depth 
WISE+NEOWISER coadds will be an important input for the Dark Energy 
Spectroscopic Instrument (DESI) selection of luminous red galaxy and quasar 
targets. Our full-depth W1/W2 coadds are already in use within the 
DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 
pipelines. Much more work still remains in order to fully leverage NEOWISER 
imaging for astrophysical applications beyond the solar system.
\end{abstract}

\keywords{methods: data analysis -- surveys -- techniques: image processing}

\section{Introduction}

The Wide-field Infrared Survey Explorer \cite[WISE; ][]{wright10} has performed
a full-sky imaging survey in four broad mid-infrared bandpasses centered at 
3.4, 4.6, 12 and 22 microns, labeled W1-W4 from blue to red. WISE has 
dramatically enhanced our knowledge of the mid-infrared sky, and publicly 
released numerous catalog and imaging data products of high value to the 
astronomical community.

More specifically, WISE launched in December 2009, and undertook a seven 
month, full-sky survey in all of W1-W4 from February 2010 through August
2010. In September 2010, the solid hydrogen cryogen used to cool the W3 and W4 
instrumentation was depleted, significantly reducing the quality of W3 
imaging and rendering W4 unusable. Nevertheless, WISE continued surveying 
the sky from September 2010 to February 2011 in W1 and W2, including 
a portion of the mission referred to as NEOWISE \citep{neowise}. In February 
2011 WISE was placed in hibernation. In October 2013, WISE was reactivated, and
recommenced surveying the sky in W1 and W2. This W1/W2 survey is referred to as 
NEOWISE-Reactivation (NEOWISER) and is expected to continue until 2017.
Importantly, the NEOWISER data are of very nearly the same high quality as
pre-hibernation W1/W2 WISE imaging \citep{neowiser}.

Several data products consisting of full-sky, stacked WISE imaging
are currently available for the first 13 months of data.
The WISE team has created a set
of ``Atlas'' coadds smoothed by the point spread function (PSF)
using the first 7 months of data (the All-Sky release), and the first
13 months of data (the AllWISE release).
In an independent processing effort, \cite{lang14} has 
produced custom ``unWISE'' stacks analogous to the AllWISE Atlas images,
but at the full spatial resolution of the instrument. These unWISE
stacks are optimized for forced photometry, and have proven to be 
an important input for eBOSS target selection 
\citep{lang14b, eboss_qso, eboss_lrg}.

However, until now, no full-sky set of W1/W2 coadds combining
all pre and post reactivation exposures have existed. The primary motivation
for such a data product is the enhanced infrared depths achieved, which
will improve the utility of WISE in selecting higher-redshift 
spectroscopic targets, in particular for the upcoming
Dark Energy Spectroscopic Instrument \citep[DESI,][]{desi}. Additionally, 
folding in two additional scans of WISE data at each sky location allows 
time-dependent artifacts to be nulled, largely eliminating spatial 
nonuformities in image quality and derivative catalogs.

Here we present a new set of full-sky coadds generated by
combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
programs. These `full-depth' coadds are publicly available 
online\footnote{http://unwise.me}. In $\S$1 we briefly describe the W1/W2 
single-exposure data set on which our full-depth coadds are based. In $\S$2
we describe an empirical, custom photometric calibration we derived in order 
to combine pre and post reactivation WISE images. In $\S$3 we describe our
rejection of time-dependent artifacts, particularly off-axis Moon 
contamination. In $\S$4 we describe our strategy for recovering 
Moon-contaminated exposures. In $\S$5 we highlight some important aspects 
of the full-sky set of full-depth coadds generated by our processing. In 
$\S$6, we present a preliminary investigation of the improvements in WISE 
depth which have resulted from doubling the amount of W1/W2 imaging. We 
conclude in $\S$7 with a brief discussion of future uses of our present 
WISE+NEOWISER coadds, as well as remaining work to be done with existing and 
future NEOWISER imaging.

% mention DECaLS in intro and add footnote to legacysurvey website

%In the remainder of this proposal, we will refer to the data from the
%first 13 months of the mission as simply ``WISE'', in contrast to
%data from the current ``NEOWISER'' mission phase.

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products. 
}

\bibliographystyle{apj}
\bibliography{fulldepth_neo1.bib}

\end{document}

### 2016-02-28 ms.tex
first draft of data section; added more references and outline

@@
 
-\altaffiltext{1}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, USA}
-\altaffiltext{2}{Lawrence Berkeley National Laboratory, Berkeley, CA, 94720, USA}
-\altaffiltext{3}{Department of Astronomy \& Astrophysics and Dunlap Institute, University of Toronto, Toronto, ON M5S 3H4, Canada}
+\altaffiltext{1}{Berkeley Center for Cosmological Physics, Berkeley, CA 94720, 
+USA}
+\altaffiltext{2}{Lawrence Berkeley National Laboratory, Berkeley, CA, 94720, 
+USA}
+\altaffiltext{3}{Department of Astronomy \& Astrophysics and Dunlap Institute, 
+University of Toronto, Toronto, ON M5S 3H4, Canada}
 
@@
 
-Several data products consisting of full-sky, stacked WISE imaging
-are currently available for the first 13 months of data.
-The WISE team has created a set
-of ``Atlas'' coadds smoothed by the point spread function (PSF)
-using the first 7 months of data (the All-Sky release), and the first
-13 months of data (the AllWISE release).
-In an independent processing effort, \cite{lang14} has 
-produced custom ``unWISE'' stacks analogous to the AllWISE Atlas images,
-but at the full spatial resolution of the instrument. These unWISE
-stacks are optimized for forced photometry, and have proven to be 
-an important input for eBOSS target selection 
-\citep{lang14b, eboss_qso, eboss_lrg}.
+Several data products consisting of full-sky, stacked WISE imaging are 
+currently available for the first 13 months of data. The WISE team has created 
+a set of ``Atlas'' coadds smoothed by the point spread function (PSF) using the
+first 7 months of data (the All-Sky release), and the first 13 months of data 
+(the AllWISE release). In an independent processing effort, \cite{lang14} has 
+produced custom ``unWISE'' stacks analogous to the AllWISE Atlas images, but at
+the full spatial resolution of the instrument. These unWISE stacks are 
+optimized for forced photometry, and have proven to be an important input for 
+eBOSS target selection \citep{lang14b, eboss_qso, eboss_lrg}.
 
-However, until now, no full-sky set of W1/W2 coadds combining
-all pre and post reactivation exposures have existed. The primary motivation
-for such a data product is the enhanced infrared depths achieved, which
-will improve the utility of WISE in selecting higher-redshift 
-spectroscopic targets, in particular for the upcoming
-Dark Energy Spectroscopic Instrument \citep[DESI,][]{desi}. Additionally, 
-folding in two additional scans of WISE data at each sky location allows 
-time-dependent artifacts to be nulled, largely eliminating spatial 
-nonuformities in image quality and derivative catalogs.
+However, until now, no full-sky set of W1/W2 coadds combining all pre and post 
+reactivation exposures have existed. The primary motivation for such a data 
+product is the enhanced infrared depths achieved, which will improve the 
+utility of WISE in selecting higher-redshift spectroscopic targets, in 
+particular for the upcoming Dark Energy Spectroscopic Instrument 
+\citep[DESI,][]{desi}. Additionally, folding in two additional scans of WISE 
+data at each sky location allows time-dependent artifacts to be nulled, largely
+eliminating spatial nonuformities in image quality and derivative catalogs.
 
@@
 programs. These `full-depth' coadds are publicly available 
-online\footnote{http://unwise.me}. In $\S$1 we briefly describe the W1/W2 
-single-exposure data set on which our full-depth coadds are based. In $\S$2
-we describe an empirical, custom photometric calibration we derived in order 
-to combine pre and post reactivation WISE images. In $\S$3 we describe our
-rejection of time-dependent artifacts, particularly off-axis Moon 
-contamination. In $\S$4 we describe our strategy for recovering 
-Moon-contaminated exposures. In $\S$5 we highlight some important aspects 
-of the full-sky set of full-depth coadds generated by our processing. In 
-$\S$6, we present a preliminary investigation of the improvements in WISE 
-depth which have resulted from doubling the amount of W1/W2 imaging. We 
-conclude in $\S$7 with a brief discussion of future uses of our present 
+online\footnote{http://unwise.me}. In $\S$\ref{sec:data} we briefly describe 
+the W1/W2 single-exposure data set on which our full-depth coadds are based. 
+In $\S$\ref{sec:calib} we describe an empirical, custom photometric calibration
+we derived in order to combine pre and post reactivation WISE images. In 
+$\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
+particularly off-axis Moon contamination. In $\S$\ref{sec:recover} we describe
+our strategy for recovering Moon-contaminated exposures. In 
+$\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
+of full-depth coadds generated by our processing. In $\S$\ref{sec:depth}, we 
+present a preliminary investigation of the improvements in WISE depth which 
+have resulted from doubling the amount of W1/W2 imaging. We conclude in 
+$\S$\ref{sec:future} with a brief discussion of future uses of our present 
 WISE+NEOWISER coadds, as well as remaining work to be done with existing and 
@@
 
-% mention DECaLS in intro and add footnote to legacysurvey website
+\section{Data}
+\label{sec:data}
 
-%In the remainder of this proposal, we will refer to the data from the
-%first 13 months of the mission as simply ``WISE'', in contrast to
-%data from the current ``NEOWISER'' mission phase.
+The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images form the basis
+for our W1/W2 coadds. Specifically, for each L1b frameset, we make use of the 
+per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, which respectively
+give the measured sky intensity and associated per-pixel bitmask values and 
+uncertainty estimates. We have obtained a local copy of these files for every 
+W1 and W2 frameset, including those from the AllWISE release ($\sim$2.9M 
+framesets) and first-year NEOWISER release ($\sim$2.5M framesets). In
+total we have analyzed $\sim$5.4M framesets in each of W1 and W2, corresponding
+to a total of $\sim$32M L1b image files and $\sim$71TB of pixel data.
+
+In addition to L1b images, we also make use of several official WISE
+catalog-level data products. During the photometric calibration described
+in $\S$\ref{sec:calib}, we select sources to photometer based on the AllWISE 
+Source Catalog \citep{cutri13}. Also, to flag and reject bright solar system 
+planets ($\S$\ref{sec:moon}), we make use of the WISE Known Solar System Object
+Possible Association List for each mission phase 
+\citep{cutri12, cutri13,cutri15}.
+
+% mention that we use the allwise source catalog during the photometric
+% mention that we also use the various ``known solar system possible 
+% association list'' catalogs
+
+\section{Custom Photometric Calibration}
+\label{sec:calib}
+
+\section{Removing Time-dependent Artifacts}
+\label{sec:moon}
+
+\section{Recovering Contaminated Frames}
+\label{sec:recover}
+
+\section{Overview of Results}
+\label{sec:results}
+
+\section{Preliminary Depth Characterization}
+\label{sec:depth}
+
+\section{Conclusion \& Future Work}
+\label{sec:future}
+
+% add footnote to legacysurvey website in section that compares
+% wise depths in DECaLS DR1 versus DR2
 
@@
 
+% cite software packages such as numpy, scipy, matplotlib ??
+
 \end{document}

### 2016-02-28 ms.tex
most of photometric calibration text added

@@
 \label{sec:calib}
+In order to combine frames across multiple mission phases, it is necessary
+to place all exposures on a common photometric calibration such that
+the multiplicative scalings of all images are consistent. Each L1b
+image includes a \verb|MAGZP| header keyword which gives the official
+Vega zero-point of that exposure. These zero-points are essentially
+predictions of system throughput based on predictors such as beam splitter
+assembly temperature, and have been shown to differ by up to several percent 
+from time-dependent gain variations measured empirically with single-exposure
+photometry of standard sources \citep{cutri13, cutri15}.
+
+We therefore sought to achieve an empirical photometric calibration
+across all mission phases accurate at the several mmag level. Our basic
+strategy was to analyze repeat measurements of compact sources near the 
+ecliptic poles, where WISE gathers data every $\sim$$95$ minutes throughout the 
+entire mission. Specifically, our sample consists of moderately bright,
+unsaturated compact sources with $|\beta| > 85^{\circ}$, and avoiding a wedge 
+defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ to exclude the LMC. The 
+positions and nominal average magnitudes of our moderately bright source
+sample were drawn from the AllWISE Source Catalog, selecting sources with 
+10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ \verb|w2mpro| $<$ 11.7 and with
+\verb|w?cc_map|=0 in the band of interest.
+
+These spatial, magnitude and flag cuts yield samples of $\sim$109,000 
+($\sim$27,000) unique calibrator sources in W1 (W2). We perform aperture 
+photometry using \verb|djs_phot| with a 27.5$''$ radius for each calibrator 
+source in every L1b exposure in which it appears sufficiently far from the 
+image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
+single-epoch aperture fluxes which form the basis for our derived 
+time-dependent zero points. The typical calibrator source contributes 
+$\gtrsim$400 epochs of photometry.
+
+We sought a photometic calibration with time resolution of one day. 
+% mention that single-epoch fluxes grouped into one-day bins
+% mention that single-epoch fluxes of each source were normalized
+% to the average (median?) flux measured during the All-sky phase, and 
+% that the AllWISE phase zero points were taken at face value, and
+% that we used the single-exp ecl pole photometry to verify that the zero point 
+% was stable at the $<=1 mmag$ level of the All-sky phase of the mission
+
+Figure 1 shows our derived zero points for each WISE mission phase as 
+compared to the \verb|MAGZP| values obtained from the L1b headers. When
+using our custom zero points to scale L1b images, we employ an 
+interpolation scheme based on a series of tapered polynomials and 
+error functions, meant to smooth out noise in our per-day zero point
+determinations. In general, our per-day zero points agree reasonably
+well with the \verb|MAGZP| values, although there are often 
+percent-level differences, and at times disagreement at the several percent
+level. In some cases the time-trends within a particular mission phase
+show qualitative disagreement (e.g. both W1 and W2 during the NEOWISE
+mission phase).
+
+% do i want to mention comparison between ecliptic north and south poles ??
+
+% caption of zero point figure needs to clarify the '4band', '3band', '2band' ..
+% terminology
 
@@
 We thank Roc Cutri for his guidance in making use of the WISE data products.
-}
+
+This research made use of the NASA Astrophysics Data System (ADS) and the IDL 
+Astronomy User's Library at Goddard. \footnote{Available at 
+\texttt{http://idlastro.gsfc.nasa.gov}}
+
+This research makes use of data products from the Wide-field Infrared
+Survey Explorer, which is a joint project of the University of California, Los
+Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
+funded by the National Aeronautics and Space Administration. This publication
+also makes use of data products from NEOWISE, which is a project of the Jet
+Propulsion Laboratory/California Institute of Technology, funded by the
+Planetary Science Division of the National Aeronautics and Space
+Administration. }
 
@@
 % cite software packages such as numpy, scipy, matplotlib ??
+% mention idlutils
 

### 2016-02-28 ms.tex
filled in photometric calibration text

@@
 
-We therefore sought to achieve an empirical photometric calibration
+We therefore sought to achieve an empirical relative photometric calibration
 across all mission phases accurate at the several mmag level. Our basic
@@
 image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
-single-epoch aperture fluxes which form the basis for our derived 
-time-dependent zero points. The typical calibrator source contributes 
+single-epoch aperture fluxes (in units of DN) which form the basis for our 
+derived time-dependent zero points. The typical calibrator source contributes 
 $\gtrsim$400 epochs of photometry.
 
-We sought a photometic calibration with time resolution of one day. 
-% mention that single-epoch fluxes grouped into one-day bins
-% mention that single-epoch fluxes of each source were normalized
-% to the average (median?) flux measured during the All-sky phase, and 
-% that the AllWISE phase zero points were taken at face value, and
-% that we used the single-exp ecl pole photometry to verify that the zero point 
-% was stable at the $<=1 mmag$ level of the All-sky phase of the mission
+We sought a photometic calibration with time resolution of one day. We
+grouped the photometric measurements in two ways. For each unique source,
+we lumped all of its All-sky phase measurements together to obtain its median
+flux (DN) in our aperture photometry system during this phase. This is
+justified because the All-sky release photometric zero points are known
+to be remarkably stable. Indeed, using our ecliptic pole singe-exposure 
+photometry database, we were able to confirm that the All-sky phase zero point 
+was stable at the $\le$2 mmag level in each band. For every aperture
+flux after the All-sky phase, we calculated a gain enhancement factor
+implied by that measurement relative to the appropriate sources
+median All-sky phase flux. We then grouped these gain enhancement factors
+into one-day bins, and quoted the median per bin as the multiplicative
+change in zero point relative to the All-sky zero point. We took the 
+All-sky zero points (20.752 in W1 and 19.596 in W2) at face value.
 

### 2016-02-28 ms.tex
finished time-dependent artifacts section; added section with unWISE framework overview; other changes

--- 2016-02-28 ms.tex
@@
 applications, including target selection for upcoming spectroscopic cosmology 
-surveys, discovery of massive galaxy clusters at high redshift, and 
+surveys, discovery of distant/massive galaxy clusters, and 
 identification of high-redshift quasars. In particular, our full-depth 
@@
 However, until now, no full-sky set of W1/W2 coadds combining all pre and post 
-reactivation exposures have existed. The primary motivation for such a data 
-product is the enhanced infrared depths achieved, which will improve the 
-utility of WISE in selecting higher-redshift spectroscopic targets, in 
-particular for the upcoming Dark Energy Spectroscopic Instrument 
-\citep[DESI,][]{desi}. Additionally, folding in two additional scans of WISE 
-data at each sky location allows time-dependent artifacts to be nulled, largely
-eliminating spatial nonuformities in image quality and derivative catalogs.
+reactivation exposures has existed. The primary motivation for such a data 
+product is the enhanced infrared depths achieved, which, among
+other benefits, will improve the utility of WISE in selecting higher-redshift 
+spectroscopic targets, in particular for the upcoming Dark Energy Spectroscopic
+Instrument \citep[DESI,][]{desi}. Additionally, folding in two additional scans
+of WISE data at each sky location allows time-dependent artifacts to be nulled,
+largely eliminating spatial nonuformities in image quality and derivative 
+catalogs.
+
+% add sentence to above paragraph about Faherty arxiv survey saying
+% WISE+NEOWISER coadds are highly valuable ?
 
@@
 combining all publicly available W1/W2 exposures from the AllWISE and NEOWISER
-programs. These `full-depth' coadds are publicly available 
-online\footnote{http://unwise.me}. In $\S$\ref{sec:data} we briefly describe 
-the W1/W2 single-exposure data set on which our full-depth coadds are based. 
-In $\S$\ref{sec:calib} we describe an empirical, custom photometric calibration
-we derived in order to combine pre and post reactivation WISE images. In 
+programs, using an adaptation of the \cite{lang14} unWISE methodology. These 
+`full-depth' coadds are publicly available online\footnote{http://unwise.me}.
+
+In $\S$\ref{sec:data} we briefly describe the W1/W2 single-exposure data set 
+from which our coadds are constructed. In $\S$\ref{sec:coadd}, we review the 
+important aspects of the unWISE coaddition framework we employ and list the 
+processing steps which are newly introduced in this work. In 
+$\S$\ref{sec:calib} we describe an empirical, custom photometric calibration we
+derived in order to combine pre and post reactivation WISE images. In 
 $\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
 particularly off-axis Moon contamination. In $\S$\ref{sec:recover} we describe
-our strategy for recovering Moon-contaminated exposures. In 
+our procedure for recovering Moon-contaminated exposures. In 
 $\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
@@
 
-The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images form the basis
-for our W1/W2 coadds. Specifically, for each L1b frameset, we make use of the 
-per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, which respectively
-give the measured sky intensity and associated per-pixel bitmask values and 
-uncertainty estimates. We have obtained a local copy of these files for every 
-W1 and W2 frameset, including those from the AllWISE release ($\sim$2.9M 
-framesets) and first-year NEOWISER release ($\sim$2.5M framesets). In
-total we have analyzed $\sim$5.4M framesets in each of W1 and W2, corresponding
-to a total of $\sim$32M L1b image files and $\sim$71TB of pixel data.
+The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
+the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
+make use of the per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, 
+which respectively give the measured sky intensity and associated per-pixel 
+bitmask values and uncertainty estimates. We have obtained a local copy of 
+these files for every W1 and W2 frameset, including those from the AllWISE 
+release ($\sim$2.9M framesets) and first-year NEOWISER release ($\sim$2.5M 
+framesets). In total we have analyzed $\sim$5.4M framesets in each of W1 and 
+W2, corresponding to a total of $\sim$32M L1b image files and $\sim$71TB of 
+pixel data.
 
-In addition to L1b images, we also make use of several official WISE
-catalog-level data products. During the photometric calibration described
-in $\S$\ref{sec:calib}, we select sources to photometer based on the AllWISE 
+% would be fun to say how many pixels of input there are total
+
+In addition to L1b images, we also make use of several catalog-level WISE
+data products. During the photometric calibration described in 
+$\S$\ref{sec:calib}, we select sources to photometer based on the AllWISE 
 Source Catalog \citep{cutri13}. Also, to flag and reject bright solar system 
-planets ($\S$\ref{sec:moon}), we make use of the WISE Known Solar System Object
+planets ($\S$\ref{sec:moon}), we employ the WISE Known Solar System Object
 Possible Association List for each mission phase 
@@
 
-% mention that we use the allwise source catalog during the photometric
-% mention that we also use the various ``known solar system possible 
-% association list'' catalogs
+\section{Image Coaddition Methodology}
+\label{sec:coadd}
+
+% should this section go before the ``data'' section ??
+
+To coadd the W1/W2 single exposures, we make use of the \cite{lang14}
+unWISE coaddition framework, and perform our image processing with an 
+adaptation of the codebase from that work. We briefly mention
+a few of the salient aspects of the unWISE coaddition methodology here; for
+a full discussion see \cite{lang14}.
+
+% mention that we use the same tile centers as Atlas and original unWISE
+Like the official WISE Atlas coadds, unWISE processing divides the sky
+into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
+arranged along iso-declination rings. Unlike the Atlas tiles, the
+unWISE code uses Lanczos interpolation to preserve the native WISE 
+angular resolution during coaddition, creating stacked outputs which are 2048 
+pixels on a side, with pixels of size 2.75$''$.
+
+During the course of this work, various modifications have been made to the
+ unWISE codebase and methodology. Here we highlight the important 
+updates/changes:
+
+\begin{itemize}
+\item We include all publicly available NEOWISER W1 and W2 exposures, 
+approximately doubling the number of input L1b frames.
+\item We adopt custom zero points based on repeat photometry at the ecliptic 
+poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
+based on the L1b header metadata.
+\item We explicitly reject exposures contaminated by the Moon and/or solar 
+system planets. No such rejection was included in the original unWISE W1/W2 
+coadds, although these and other artifacts were addressed to some extent via 
+general-purpose outlier rejection measures.
+\item In this work we attempt to recover Moon-affected frames by applying 
+polynomial background level corrections to the contaminated exposures.
+\end{itemize}
+
+The outputs generated in this work follow the same data model as those of 
+\cite{lang14}. For each tile, a stacked image is created, plus auxiliary
+maps of useful quantities such as the per-pixel inverse variance and integer 
+coverage. Both our full-depth stacks and those of \cite{lang14} have units of 
+Vega nanomaggies.
 
@@
 assembly temperature, and have been shown to differ by up to several percent 
-from time-dependent gain variations measured empirically with single-exposure
-photometry of standard sources \citep{cutri13, cutri15}.
+relative to gain variations measured empirically with single-exposure
+photometry of calibrator sources \citep{cutri13, cutri15}.
 
-We therefore sought to achieve an empirical photometric calibration
-across all mission phases accurate at the several mmag level. Our basic
-strategy was to analyze repeat measurements of compact sources near the 
-ecliptic poles, where WISE gathers data every $\sim$$95$ minutes throughout the 
-entire mission. Specifically, our sample consists of moderately bright,
-unsaturated compact sources with $|\beta| > 85^{\circ}$, and avoiding a wedge 
-defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ to exclude the LMC. The 
-positions and nominal average magnitudes of our moderately bright source
-sample were drawn from the AllWISE Source Catalog, selecting sources with 
-10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ \verb|w2mpro| $<$ 11.7 and with
-\verb|w?cc_map|=0 in the band of interest.
+We therefore sought to achieve an empirical relative photometric calibration
+across all mission phases accurate at the several mmag level. To do so, we 
+analyzed repeat measurements of compact sources near the 
+ecliptic poles, where WISE has gathered data every $\sim$$95$ minutes 
+throughout the entire mission. Specifically, our sample consists of moderately 
+bright, unsaturated compact sources with $|\beta| > 85^{\circ}$, avoiding a 
+wedge defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ near the south ecliptic
+pole to exclude the LMC. The positions and nominal average magnitudes of our 
+moderately bright source sample were drawn from the AllWISE Source Catalog, 
+selecting sources with 10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ 
+\verb|w2mpro| $<$ 11.7 and with \verb|w?cc_map|=0 in the band of interest.
 
@@
 image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
-single-epoch aperture fluxes which form the basis for our derived 
-time-dependent zero points. The typical calibrator source contributes 
-$\gtrsim$400 epochs of photometry.
+single-epoch aperture fluxes (in units of DN), which will form the basis for 
+our derived time-dependent zero points. The typical calibrator source 
+contributes $\gtrsim$400 epochs of photometry.
 
-We sought a photometic calibration with time resolution of one day. 
-% mention that single-epoch fluxes grouped into one-day bins
-% mention that single-epoch fluxes of each source were normalized
-% to the average (median?) flux measured during the All-sky phase, and 
-% that the AllWISE phase zero points were taken at face value, and
-% that we used the single-exp ecl pole photometry to verify that the zero point 
-% was stable at the $<=1 mmag$ level of the All-sky phase of the mission
+We desired a photometic calibration with time resolution of one day. To
+achieve this, we grouped our single-exposure photometric measurements in two 
+ways. First, for each 
+unique source, we lumped all of its All-Sky phase measurements together to 
+obtain its median flux (DN) in our aperture photometry system during this 
+phase. This is justified because the All-Sky release photometric zero points 
+are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
+pole singe-exposure photometry database, we were able to confirm that the 
+All-Sky phase zero point was stable at the $\le$2 mmag level in each band. 
+Next, for every aperture flux after the All-Sky phase, we calculated a 
+multiplicative enhancement factor
+implied by the ratio of that measurement to the appropriate source's
+median All-Sky phase flux. We then grouped these 
+multiplicative enhancement factors into one-day bins, and quote the median per 
+bin as the change in multiplicative
+image scaling relative to the All-Sky zero point. For the  
+All-Sky phase zero points, we adopted the \verb|MAGZP| values of 20.752 in W1 
+and 19.596 in W2.
 
@@
 
+%discuss moon first and focus on moon
+The WISE scan strategy is such that a typical sky location will be 
+observed at approximately six month intervals, with each six monthly
+``visit'' yielding a series of $\sim$12 exposures within a time span of $\sim$1
+day. During the AllWISE release, most of the sky experienced just two visits
+of W1/W2 imaging. Incorporating exposures from both the AllWISE and
+NEOWISER phases effectively doubles this value to four visits everywhere
+on the sky. If we coadded the AllWISE+NEOWISER data naively, without
+concern for time dependent artifacts, we would risk corrupting regions of the 
+sky that were pristine during the AllWISE phase. We have found that by 
+leveraging the added redundancy of extra NEOWISER visits while carefully 
+addressing time-dependent artifacts, we can create full-depth coadds which are 
+nearly artifact-free over the entire sky.
+
+The dominant time-dependent artifact in W1/W2 images is off-axis
+scattered light from the Moon, which can significantly contaminate
+images at angular separations of up to many tens of degrees. This
+contamination manifests itself in L1b exposures as a strongly spatially 
+variable background level, which in certain images can be smooth, but in
+others can show a very complex morphology.
+
+In the \cite{lang14} unWISE processing, no steps were taken specifically
+to mitigate Moon contamination in W1 and W2. However \cite{lang14} did 
+address Moon contamination in W3 and W4. \cite{lang14}
+inspected all exposures flagged with the \verb|MOON_MASKED| bit, and 
+discarded those frames with abnormally large pixel value standard deviations,
+indicative of a strongly varying background level (see \cite{lang14} $\S$2
+for full details). In the present work we have applied this same
+Moon rejection criterion to W1 and W2 frames. Because of the added redundancy
+of two extra NEOWISER scans, we are thus able to reject many W1/W2
+frames which are contaminated by moonlight, while still retaining 
+sufficient uncontaminated coverage everywhere on the sky to avoid leaving
+any holes in the stacks.
+
+Figure 2 shows the dramatic improvement achieved toward maintaining a 
+consistent coadd background level by virtue of folding in NEOWISER data and 
+applying the frame-level Moon rejection cut, for a tile with severe Moon 
+contamination during the AllWISE phase.
+
+A second, less common form of time-dependent artifact results when
+bright solar system planets (Mars, Jupiter and Saturn) pass through
+the WISE field of view. These planet sightings are prominent in the 
+\cite{lang14} unWISE stacks, as no steps were taken to address these
+occurrences. In constructing our new full-depth coadds, we have used the Known 
+Solar System Possible Association list to identify all exposures in which
+Mars, Jupiter or Saturn falls within the WISE field of view. We discard
+such frames during coaddition.
+
+These bright planets also result in scattered light halos a few degrees in size.
+Therefore, we additionally use ephemerides to identify all frames within 
+2.5$^{\circ}$ of these planets. During the standard unWISE coaddition procedure,
+such frames are discarded. However, we later attempt to recover these
+frames according to the procedure described below in $\S$\ref{sec:recover}.
+
+% figure showing single-tile example of removed moon contamination
+
 \section{Recovering Contaminated Frames}
@@
 
+% quadrant warping example figure
+
 \section{Overview of Results}
 \label{sec:results}
+
+% figure showing before/after of SGP on large scales in both W1/W2
+% figure showing close-up at low ecl latitude with reduced noise
+
+% would be fun to say how many pixels of output there are total
 

### 2016-02-28 ms.tex
first attempt at section describing recovery of Moon-contaminated frames

@@
 
+Although we were able to dramatically reduce the impact of Moon contamination
+on our coadds with the exposure rejection procedure of $\S$\ref{sec:moon},
+we would ideally like to recover as much Moon-contaminated data as possible,
+rather than simply discard it all outright. To that end, we have added an 
+after-burner step to our coaddition procedure which attempts to salvage those 
+frames which were flagged with \verb|MOON_MASKED| and displayed abnormally 
+large pixel value standard deviations. The procedure we employ is a variant of 
+that described in $\S6.4.1$ of \cite{meisner14}.
+
+The first two rounds of unWISE coaddition still proceed exactly as 
+described in \cite{lang14}. These steps yield a Moon-free stack which we 
+subsequenty use as a reference image to compare against, and derive low-order 
+corrections for, each Moon-contaminated frame.
+
+For each frame initially rejected on the basis of Moon contamination, we 
+first resample the exposure onto the coadd astrometry. We then divide
+the exposure into quadrants which we analyze separately. For each quadrant,
+we will attempt to model the Moon contamination with a polynomial 
+offset as a function of L1b $x$, $y$ pixel coordinates. We begin by masking out 
+the brightest and faintest 5\% of pixels in the reference coadd, since pixels
+with bright compact sources will not be very informative for background level
+modeling. We then fit the difference between the masked L1b quadrant and masked
+reference coadd with a fourth order polynomial in L1b $x$, $y$ coordinates. We 
+evaluate the chi-squared of this model, using the reference coadd's per-pixel
+standard deviation to construct per-pixel uncertainty estimates.
+
+For each quadrant, we deem the polynomial correction to be a satisfactory 
+description of the scattered moonlight if the mean per-pixel chi-squared is 
+less than 2.5. In that case, we then subtract the polynomial correction from 
+the quadrant, and consider the quadrant ``recovered''. Quadrants with poor 
+chi-squared are discarded and remain excluded from the coadd. Once a list of 
+all recovered quadrants has been assembled, these are accumulated into the 
+existing reference coadd to produce a final set of outputs for the tile under 
+consideration.
+
+Figure 3 provides an illustration of our polynomial background modeling
+procedure. We were able to recover 54\% of Moon-contaminated data
+in W1 and 33\% in W2. We also apply this polynomial
+correction procedure to frames that we flagged as potentially affected
+by scattered light halos from bright solar system planets.
+
 % quadrant warping example figure
@@
 We thank Roc Cutri for his guidance in making use of the WISE data products. 
+We thank Stephen Bailey for downloading the L1b images to NERSC. We thank
+Doug Finkbeiner for providing access to the big-memory computers which
+were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
+providing HPC assistance. We thank many members of the DECaLS/MzLS data team for
+valuable feedback, especially Arjun Dey, Doug Finkbeiner, John Moustakas
+and Bob Blum.
+
+This research used resources of the National Energy Research Scientific 
+Computing Center, a DOE Office of Science User Facility supported by the Office
+of Science of the U.S. Department of Energy under Contract No. 
+DE-AC02-05CH11231.
 
@@
 Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
-funded by the National Aeronautics and Space Administration. This publication
+funded by the National Aeronautics and Space Administration. This research
 also makes use of data products from NEOWISE, which is a project of the Jet

### 2016-02-28 ms.tex
first pass at results overview section

@@
 \item We include all publicly available NEOWISER W1 and W2 exposures, 
-approximately doubling the number of input L1b frames.
+approximately doubling the number of input L1b frames relative to \cite{lang14}.
 \item We adopt custom zero points based on repeat photometry at the ecliptic 
@@
 \item We explicitly reject exposures contaminated by the Moon and/or solar 
-system planets. No such rejection was included in the original unWISE W1/W2 
-coadds, although these and other artifacts were addressed to some extent via 
-general-purpose outlier rejection measures.
+system planets. No such rejection was included in the \cite{lang14} unWISE 
+W1/W2 coadds, although these and other artifacts were addressed to some extent 
+via general-purpose outlier rejection.
 \item In this work we attempt to recover Moon-affected frames by applying 
@@
 maps of useful quantities such as the per-pixel inverse variance and integer 
-coverage. Both our full-depth stacks and those of \cite{lang14} have units of 
-Vega nanomaggies.
+coverage. Like those of \cite{lang14}, our coadds have units of Vega 
+nanomaggies.
 
@@
 
+Figures 4 and 5 show large-scale renderings of our full-depth coadds 
+over the north and south Galactic caps respectively. It is 
+apparent that the Moon contamination has been completely eliminated in
+W1 and dramatically reduced in W2. It is possible that simply folding in 
+additional NEOWISER W2 frames from forthcoming data releases will diminish the 
+remaining Moon imprint to such an extent that no additional processing 
+modifications will be required to address this issue.
+
+Figure 6 shows zoom-ins of low ecliptic latitude fields which illustrate
+visually the reduction in statistical noise which has been achieved
+by doubling the number of input exposures.
+
+Given that we imposed various cuts to eliminate time-dependent artifacts,
+it is reasonable to ask whether we have created any zero-coverage holes
+as a result. We have checked all 18,240 of our integer coverage maps, and find
+that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.
+
 % figure showing before/after of SGP on large scales in both W1/W2
@@
 
+% add footnote to legacysurvey website in section that compares
+% wise depths in DECaLS DR1 versus DR2
+
 \section{Conclusion \& Future Work}
 \label{sec:future}
-
-% add footnote to legacysurvey website in section that compares
-% wise depths in DECaLS DR1 versus DR2
 

### 2016-02-28 ms.tex
placeholders for remaining sections, will need to be majorly revised

@@
 
-% add footnote to legacysurvey website in section that compares
-% wise depths in DECaLS DR1 versus DR2
+It is important to quantify the effect of increased coverage on
+the W1/W2 depths achieved by catalogs based on our AllWISE+NEOWISER coadds 
+relative to those based on the AllWISE-only coadds of \cite{lang14}. A
+full characterization should systematically explore a range of 
+ecliptic and galactic latitudes, to consider the full spectrum of interplay
+between decreased statistical noise and confusion. For isolated sources in the 
+sky noise limit, we would expect a doubling of the W1/W2 imaging data
+to increase the depth in each band by 0.38 mag.
+
+The only existing catalogs based on our AllWISE+NEOWISER W1/W2 coadds
+are forced photometry catalogs corresponding to DECam Legacy
+Survey\footnote{http://legacysurvey.org} (DECaLS) DR2 optical sources. 
+Optical sources from DECaLS DR1 are accompanied by forced based on the
+\cite{lang14} W1/W2 coadds. Therefore, comparing the S/N of W1/W2
+fluxes in DR2 versus DR1 allows us to obtain a preliminary estimate of the 
+increased depths in regions of low ecliptic and high galactic latitude.
+
+We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
+faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
+in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
+higher S/N in W1 (W2). For comparison, the expectation based purely on
+reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
+S/N.
+
+Much more work is needed to characterize the increased sensitivity
+of WISE to faint sources due to the inclusion of NEOWISER
+imaging, as this will inform forecasts about the final depths expected
+upon WISE's permanent retirement.
 
@@
 \label{sec:future}
+
+We have created a full-sky set of W1/W2 coadds which combine all publicly
+available exposures from both the AllWISE and NEOWISER releases. Doubling the 
+amount of WISE imaging relative to the AllWISE release has resulted in improved
+W1/W2 depths and allowed for the elimination of nearly all time-dependent 
+artifacts. Our new AllWISE+NEOWISER W1/W2 coadds are publicly available
+via http://unwise.me.
+
+Although the present analysis constituted a significant data processing 
+endeavor, it represents only a small fraction of the work that must
+be done to maximize science return from the NEOWISER imaging data set.
+Creation of time-resolved coadds spanning the $\sim$5 year WISE-NEOWISER
+time baseline would enable a wealth of important time-domain projects,
+ranging from brown dwarf searches to quasar variability. As
+additional years worth of NEOWISER data become publicly available, it
+will be necessary to continue updating the full-depth WISE+NEOWISER coadds
+to maximize the achieved depth. Finally, the creation WISE-only (as opposed
+to forced photometry) catalogs based on deep coadds which include
+NEOWISER images will be needed in order to enable a variety of exciting
+discoveries.
 

### 2016-02-28 ms.tex
numbers

@@
 these files for every W1 and W2 frameset, including those from the AllWISE 
-release ($\sim$2.9M framesets) and first-year NEOWISER release ($\sim$2.5M 
-framesets). In total we have analyzed $\sim$5.4M framesets in each of W1 and 
-W2, corresponding to a total of $\sim$32M L1b image files and $\sim$71TB of 
-pixel data.
+release ($\sim$2.8M framesets) and first-year NEOWISER release ($\sim$2.5M 
+framesets). In all we have analyzed $\sim$5.3M framesets in each of W1 and 
+W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
+input image data and $\sim$33$\times$10$^{12}$ pixels.
 

### 2016-02-28 ms.tex
consistent terminology

@@
 
-\shorttitle{WISE/NEOWISER Coadds}
+\shorttitle{AllWISE+NEOWISER Coadds}
 
@@
 identification of high-redshift quasars. In particular, our full-depth 
-WISE+NEOWISER coadds will be an important input for the Dark Energy 
+AllWISE+NEOWISER coadds will be an important input for the Dark Energy 
 Spectroscopic Instrument (DESI) selection of luminous red galaxy and quasar 
@@
 $\S$\ref{sec:future} with a brief discussion of future uses of our present 
-WISE+NEOWISER coadds, as well as remaining work to be done with existing and 
+AllWISE+NEOWISER coadds, as well as remaining work to be done with existing and 
 future NEOWISER imaging.
@@
 additional years worth of NEOWISER data become publicly available, it
-will be necessary to continue updating the full-depth WISE+NEOWISER coadds
+will be necessary to continue updating the full-depth AllWISE+NEOWISER coadds
 to maximize the achieved depth. Finally, the creation WISE-only (as opposed

### 2016-02-29 ms.tex
added figure showing Moon clean-up for an example tile

@@
 
+\begin{figure*}
+ \begin{center}
+  \epsfig{file=moon_3433p000.eps, width=6.5in}
+  \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
+           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
+           ecliptic latitude which experienced strong Moon contamination 
+           during the AllWISE mission phase. Rejecting Moon-contaminated
+           frames as described in \ref{sec:moon} while including
+           two extra visits worth of NEOWISER data has dramatically
+           improved the background level uniformity relative to the
+           \cite{lang14} version of this tile. For this tile, we were
+           able to recover 58\% (18\%) of frames in W1 (W2).}
+ \end{center}
+\end{figure*}
+
 A second, less common form of time-dependent artifact results when

### 2016-02-29 ms.tex
properly reference Moon tile figure

@@
 
-Figure 2 shows the dramatic improvement achieved toward maintaining a 
-consistent coadd background level by virtue of folding in NEOWISER data and 
-applying the frame-level Moon rejection cut, for a tile with severe Moon 
-contamination during the AllWISE phase.
+Figure \ref{fig:moon_3433p000} shows the dramatic improvement achieved toward 
+maintaining a consistent coadd background level by virtue of folding in 
+NEOWISER data and applying the frame-level Moon rejection cut, for a tile with 
+severe Moon contamination during the AllWISE phase.
 

### 2016-02-29 ms.tex
image noise figure

@@
 
+\begin{figure}
+ \begin{center}
+  \epsfig{file=w1_image_noise.eps, width=3.0in}
+  \caption{\label{fig:image_noise} Illustration of reduced image noise
+           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
+           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
+           This is a representative location at low ecliptic latitude and high 
+           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
+           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
+           images are rendered with identical color stretches.}
+ \end{center}
+\end{figure}
+
 Given that we imposed various cuts to eliminate time-dependent artifacts,

### 2016-02-29 ms.tex
added quadrant warp example figure

@@
 
-% figure showing single-tile example of removed moon contamination
-
 \section{Recovering Contaminated Frames}
@@
 
-Figure 3 provides an illustration of our polynomial background modeling
-procedure. We were able to recover 54\% of Moon-contaminated data
-in W1 and 33\% in W2. We also apply this polynomial
+Figure \ref{fig:warp_example} provides an illustration of our polynomial 
+background modeling procedure. We were able to recover 54\% of 
+Moon-contaminated data in W1 and 33\% in W2. We also apply this polynomial
 correction procedure to frames that we flagged as potentially affected
@@
 % quadrant warping example figure
+
+\begin{figure*}
+ \begin{center}
+  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
+  \caption{\label{fig:warp_example} Illustration of the procedure by which
+           we recover Moon-contaminated exposures, as described in 
+           $\S$\ref{sec:recover}. Shown here is quadrant 2
+           of W1 exposure 05245b140. This quadrant was successfully recovered.}
+% mention which tile used as reference?
+ \end{center}
+\end{figure*}
 
@@
 
-Figure 6 shows zoom-ins of low ecliptic latitude fields which illustrate
-visually the reduction in statistical noise which has been achieved
-by doubling the number of input exposures.
+Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
+which illustrate visually the reduction in statistical noise which has been 
+achieved by doubling the number of input exposures.
+
+% figure showing close-up at low ecl latitude with reduced noise
 
@@
 % figure showing before/after of SGP on large scales in both W1/W2
-% figure showing close-up at low ecl latitude with reduced noise
-
-% would be fun to say how many pixels of output there are total
 

### 2016-02-29 ms.tex
attempted to force figures to be in certain places, added photometric calibration figure

@@
 
+\begin{figure*} [ht]
+ \begin{center}
+  \epsfig{file=zp_by_day.eps, width=7.0in}
+  \caption{\label{fig:zp} Zero point calibration results.}
+ \end{center}
+\end{figure*}
+
 We desired a photometic calibration with time resolution of one day. To
@@
 
-Figure 1 shows our derived zero points for each WISE mission phase as 
-compared to the \verb|MAGZP| values obtained from the L1b headers. When
+Figure \ref{fig:zp} shows our derived zero points for each WISE mission phase 
+as compared to the \verb|MAGZP| values obtained from the L1b headers. When
 using our custom zero points to scale L1b images, we employ an 
@@
 
+\begin{figure*} [ht]
+ \begin{center}
+  \epsfig{file=moon_3433p000.eps, width=6.5in}
+  \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
+           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
+           ecliptic latitude which experienced strong Moon contamination 
+           during the AllWISE mission phase. Rejecting Moon-contaminated
+           frames as described in \ref{sec:moon} while including
+           two extra visits worth of NEOWISER data has dramatically
+           improved the background level uniformity relative to the
+           \cite{lang14} version of this tile. For this tile, we were
+           able to recover 58\% (18\%) of frames in W1 (W2).}
+ \end{center}
+\end{figure*}
+
 In the \cite{lang14} unWISE processing, no steps were taken specifically
@@
 
-\begin{figure*}
- \begin{center}
-  \epsfig{file=moon_3433p000.eps, width=6.5in}
-  \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
-           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
-           ecliptic latitude which experienced strong Moon contamination 
-           during the AllWISE mission phase. Rejecting Moon-contaminated
-           frames as described in \ref{sec:moon} while including
-           two extra visits worth of NEOWISER data has dramatically
-           improved the background level uniformity relative to the
-           \cite{lang14} version of this tile. For this tile, we were
-           able to recover 58\% (18\%) of frames in W1 (W2).}
- \end{center}
-\end{figure*}
-
 A second, less common form of time-dependent artifact results when
@@
 \label{sec:recover}
+
+% quadrant warping example figure
+
+\begin{figure*}[ht]
+ \begin{center}
+  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
+  \caption{\label{fig:warp_example} Illustration of the procedure by which
+           we recover Moon-contaminated exposures, as described in 
+           $\S$\ref{sec:recover}. Shown here is quadrant 2
+           of W1 exposure 05245b140. This quadrant was successfully recovered.}
+% mention which tile used as reference?
+ \end{center}
+\end{figure*}
 
@@
 by scattered light halos from bright solar system planets.
-
-% quadrant warping example figure
-
-\begin{figure*}
- \begin{center}
-  \epsfig{file=05245b140_w1_q2.eps, width=7.0in}
-  \caption{\label{fig:warp_example} Illustration of the procedure by which
-           we recover Moon-contaminated exposures, as described in 
-           $\S$\ref{sec:recover}. Shown here is quadrant 2
-           of W1 exposure 05245b140. This quadrant was successfully recovered.}
-% mention which tile used as reference?
- \end{center}
-\end{figure*}
 

### 2016-02-29 ms.tex
various edits

@@
 \label{sec:calib}
+
 In order to combine frames across multiple mission phases, it is necessary
-to place all exposures on a common photometric calibration such that
-the multiplicative scalings of all images are consistent. Each L1b
-image includes a \verb|MAGZP| header keyword which gives the official
+to place all exposures on a common photometric calibration so that
+the multiplicative scalings of all input images are consistent. Each L1b
+image includes a \verb|MAGZP| header keyword which gives the nominal
 Vega zero-point of that exposure. These zero-points are essentially
 predictions of system throughput based on predictors such as beam splitter
-assembly temperature, and have been shown to differ by up to several percent 
-relative to gain variations measured empirically with single-exposure
+assembly temperature, and have been found to differ by up to several percent 
+relative to zero point variations measured empirically with single-exposure
 photometry of calibrator sources \citep{cutri13, cutri15}.
 
-We therefore sought to achieve an empirical relative photometric calibration
-across all mission phases accurate at the several mmag level. To do so, we 
+% ^ list exact exp. supp. section that discusses this
+
+We therefore sought to derive an empirical relative photometric calibration
+across all mission phases accurate at the sub-percent level. To do so, we 
 analyzed repeat measurements of compact sources near the 
@@
   \epsfig{file=zp_by_day.eps, width=7.0in}
-  \caption{\label{fig:zp} Zero point calibration results.}
+  \caption{\label{fig:zp} In each panel, the red dashes give the per-day
+           photometric zero points we derived based on repeat measurements
+           of stars near the ecliptic poles, as described in 
+           $\S$\ref{sec:calib}. The black lines show the
+           \texttt{MAGZP} zero point values provided by the L1b header 
+           metadata. The magenta (green) dashes
+           represent the zero point time trends which would have resulted had
+           we restricted our analysis to aperture photometry of only the north 
+           (south) ecliptic pole.}
  \end{center}
@@
 pole singe-exposure photometry database, we were able to confirm that the 
-All-Sky phase zero point was stable at the $\le$2 mmag level in each band. 
+All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
 Next, for every aperture flux after the All-Sky phase, we calculated a 
@@
 Figure \ref{fig:zp} shows our derived zero points for each WISE mission phase 
-as compared to the \verb|MAGZP| values obtained from the L1b headers. When
-using our custom zero points to scale L1b images, we employ an 
-interpolation scheme based on a series of tapered polynomials and 
-error functions, meant to smooth out noise in our per-day zero point
-determinations. In general, our per-day zero points agree reasonably
+as compared to the \verb|MAGZP| values obtained from the L1b headers.  
+In general, our per-day zero points agree reasonably
 well with the \verb|MAGZP| values, although there are often 
 percent-level differences, and at times disagreement at the several percent
-level. In some cases the time-trends within a particular mission phase
-show qualitative disagreement (e.g. both W1 and W2 during the NEOWISE
-mission phase).
-
-% do i want to mention comparison between ecliptic north and south poles ??
+level. In some cases the empirically measured time trends within a particular 
+mission phase show qualitative disagreement with the header metadata (e.g. both
+the W1 and W2 zero points during the NEOWISE mission phase). When scaling each
+L1b image according to its zero point during coaddition, we employ an 
+interpolation scheme meant to avoid directly using our somewhat noisy per-day 
+measurements. Specifically, we create a smooth approximate representation of 
+the measured per-day zero point time-series, based on a series of polynomials 
+and error functions, tapering between segments such that the resulting curve is
+ smooth.
 
@@
 address Moon contamination in W3 and W4. \cite{lang14}
-inspected all exposures flagged with the \verb|MOON_MASKED| bit, and 
+inspected all W3/W4 exposures flagged with the \verb|MOON_MASKED| bit, and 
 discarded those frames with abnormally large pixel value standard deviations,
@@
 
-A second, less common form of time-dependent artifact results when
+A second, less common type of time-dependent artifact results when
 bright solar system planets (Mars, Jupiter and Saturn) pass through
 the WISE field of view. These planet sightings are prominent in the 
-\cite{lang14} unWISE stacks, as no steps were taken to address these
+\cite{lang14} unWISE stacks, as no steps were taken to address such
 occurrences. In constructing our new full-depth coadds, we have used the Known 
 Solar System Possible Association list to identify all exposures in which
-Mars, Jupiter or Saturn falls within the WISE field of view. We discard
-such frames during coaddition.
+Mars, Jupiter or Saturn fall within the WISE field of view. We discard
+such frames completely during coaddition and make no attempt to recover them.
 
-These bright planets also result in scattered light halos a few degrees in size.
-Therefore, we additionally use ephemerides to identify all frames within 
-2.5$^{\circ}$ of these planets. During the standard unWISE coaddition procedure,
-such frames are discarded. However, we later attempt to recover these
+Bright planets are also accompanied by scattered light halos a few degrees in 
+size. Therefore, we additionally use ephemerides to identify all frames within 
+2.5$^{\circ}$ of these planets. During coaddition,
+such frames are initially ignored. However, we later attempt to recover such
 frames according to the procedure described below in $\S$\ref{sec:recover}.
@@
 of WISE to faint sources due to the inclusion of NEOWISER
-imaging, as this will inform forecasts about the final depths expected
-upon WISE's permanent retirement.
+imaging, as this will inform forecasts about the final 3.4$\mu$m and 
+4.6$\mu$m depths expected upon WISE's permanent retirement.
 
@@
 be done to maximize science return from the NEOWISER imaging data set.
-Creation of time-resolved coadds spanning the $\sim$5 year WISE-NEOWISER
+Creation of time-resolved coadds spanning the $\sim$5 year AllWISE-NEOWISER
 time baseline would enable a wealth of important time-domain projects,
-ranging from brown dwarf searches to quasar variability. As
+ranging from brown dwarf searches to IR quasar variability studies. As
 additional years worth of NEOWISER data become publicly available, it
 will be necessary to continue updating the full-depth AllWISE+NEOWISER coadds
-to maximize the achieved depth. Finally, the creation WISE-only (as opposed
-to forced photometry) catalogs based on deep coadds which include
-NEOWISER images will be needed in order to enable a variety of exciting
+to maximize the achieved W1/W2 depths. Finally, the creation WISE-only (as 
+opposed to forced photometry) catalogs based on deep coadds which incorporate
+NEOWISER images will be needed to enable a variety of exciting
 discoveries.

### 2016-02-29 ms.tex
added W2 SGC figure

@@
 
+\begin{figure*} [ht]
+ \begin{center}
+  \epsfig{file=w2_large_scale.eps, width=7.0in}
+  \caption{\label{fig:w2_large} A large portion of the south Galactic
+           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
+           unWISE coadds based on the AllWISE release imaging and without
+           rejection of Moon-contaminated frames. Bottom: same region of
+           sky in our new AllWISE+NEOWISER stacks, with double the
+           redundancy in sky coverage and rejection/recovery of 
+           Moon-contaminated frames.}
+ \end{center}
+\end{figure*}
+% should state approximate bounding coords in terms of lambda, beta
+
 Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
@@
 
-\begin{figure}
+\begin{figure}[ht]
  \begin{center}
@@
 
-Given that we imposed various cuts to eliminate time-dependent artifacts,
-it is reasonable to ask whether we have created any zero-coverage holes
-as a result. We have checked all 18,240 of our integer coverage maps, and find
-that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.
+Given that we imposed various frame-level cuts to eliminate time-dependent 
+artifacts, it is reasonable to ask whether we have created any zero-coverage 
+holes as a result. We have checked all 18,240 of our integer coverage maps, and
+find that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.
 
@@
 via http://unwise.me.
+
+% could list future improvement's i'd like to implement for NEO(2+) coadds
+% for instance masking of bright star ghosts and correction
+% of bright star scattered light, possibly creation of a bitmask output
+% like that of meisner/finkbeiner dust coadds
+% also min/max removal step as added protection against outliers
 

### 2016-02-29 ms.tex
minor edits

@@
 
-To coadd the W1/W2 single exposures, we make use of the \cite{lang14}
+To stack the W1/W2 single exposures, we make use of the \cite{lang14}
 unWISE coaddition framework, and perform our image processing with an 
@@
 into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
-arranged along iso-declination rings. Unlike the Atlas tiles, the
+arranged along iso-declination rings. Unlike the Atlas stacks, the
 unWISE code uses Lanczos interpolation to preserve the native WISE 
 angular resolution during coaddition, creating stacked outputs which are 2048 
-pixels on a side, with pixels of size 2.75$''$.
+pixels on a side, with 2.75$''$ pixels.
 
@@
 \item We include all publicly available NEOWISER W1 and W2 exposures, 
-approximately doubling the number of input L1b frames relative to \cite{lang14}.
+approximately doubling the number of input L1b frames relative to the 
+\cite{lang14} processing.
 \item We adopt custom zero points based on repeat photometry at the ecliptic 
@@
 The outputs generated in this work follow the same data model as those of 
-\cite{lang14}. For each tile, a stacked image is created, plus auxiliary
-maps of useful quantities such as the per-pixel inverse variance and integer 
-coverage. Like those of \cite{lang14}, our coadds have units of Vega 
+\cite{lang14}. For each tile, a stacked intensity image is created, as well as
+auxiliary maps of useful quantities such as the per-pixel inverse variance and
+integer coverage. Like those of \cite{lang14}, our coadds have units of Vega 
 nanomaggies.
@@
 
-Although we were able to dramatically reduce the impact of Moon contamination
+Although we are able to dramatically reduce the impact of Moon contamination
 on our coadds with the exposure rejection procedure of $\S$\ref{sec:moon},
@@
 
-Figures 4 and 5 show large-scale renderings of our full-depth coadds 
-over the north and south Galactic caps respectively. It is 
+Figures \ref{fig:w2_large} and 5 show large-scale renderings of our full-depth 
+coadds over the north and south Galactic caps respectively. It is 
 apparent that the Moon contamination has been completely eliminated in
@@
            redundancy in sky coverage and rejection/recovery of 
-           Moon-contaminated frames.}
+           Moon-contaminated frames. It is clear that the scattered
+           moonlight has been largely removed in W2, although 
+           some traces still remain.}
  \end{center}

### 2016-02-29 ms.tex
added W1 large-scale map figure

@@
 
-Figures \ref{fig:w2_large} and 5 show large-scale renderings of our full-depth 
-coadds over the north and south Galactic caps respectively. It is 
-apparent that the Moon contamination has been completely eliminated in
+Figures \ref{fig:w2_large} and \ref{fig:w1_large} show large-scale renderings 
+of our full-depth coadds over the north and south Galactic caps respectively. 
+It is apparent that the Moon contamination has been completely eliminated in
 W1 and dramatically reduced in W2. It is possible that simply folding in 
@@
 
+\begin{figure*} [ht]
+ \begin{center}
+  \epsfig{file=w1_large_scale.eps, width=7.0in}
+  \caption{\label{fig:w1_large} A sub-section of the region shown in Figure
+           \ref{fig:w2_large}. Top: \cite{lang14}
+           unWISE coadds based on the AllWISE release imaging and without
+           rejection of Moon-contaminated frames. Bottom: same region of
+           sky in our new AllWISE+NEOWISER stacks, with double the
+           redundancy in sky coverage and rejection/recovery of 
+           Moon-contaminated frames. Scattered moonlight has effectively
+           been completely eliminated in W1.}
+ \end{center}
+\end{figure*}
+
 Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
@@
 
-\begin{figure}[ht]
+\begin{figure*}[ht]
  \begin{center}
-  \epsfig{file=w1_image_noise.eps, width=3.0in}
-  \caption{\label{fig:image_noise} Illustration of reduced image noise
+  \epsfig{file=w1_image_noise.eps, width=6.0in}
+  \caption{\label{fig:image_noise} Example of reduced image noise
            in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
@@
  \end{center}
-\end{figure}
+\end{figure*}
 

### 2016-02-29 ms.tex
various minor edits

@@
 bitmask values and uncertainty estimates. We have obtained a local copy of 
-these files for every W1 and W2 frameset, including those from the AllWISE 
-release ($\sim$2.8M framesets) and first-year NEOWISER release ($\sim$2.5M 
-framesets). In all we have analyzed $\sim$5.3M framesets in each of W1 and 
-W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
+these files for every publicly available W1 and W2 frameset, including those 
+from the AllWISE release ($\sim$2.8M framesets) and first-year NEOWISER release
+($\sim$2.5M framesets). In all we have analyzed $\sim$5.3M framesets in each of
+W1 and W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
 input image data and $\sim$33$\times$10$^{12}$ pixels.
@@
 into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
-arranged along iso-declination rings. Unlike the Atlas stacks, the
-unWISE code uses Lanczos interpolation to preserve the native WISE 
-angular resolution during coaddition, creating stacked outputs which are 2048 
-pixels on a side, with 2.75$''$ pixels.
+arranged along iso-declination rings. Whereas the Atlas images
+are smoothed by the WISE PSF, the unWISE code uses Lanczos interpolation to 
+preserve the native WISE angular resolution during coaddition, creating stacked
+outputs which are 2048 pixels on a side, with 2.75$''$ pixels.
 
@@
 We desired a photometic calibration with time resolution of one day. To
-achieve this, we grouped our single-exposure photometric measurements in two 
-ways. First, for each 
+achieve this, we grouped our single-exposure aperture photometry measurements 
+in two ways. First, for each 
 unique source, we lumped all of its All-Sky phase measurements together to 
@@
 Figure \ref{fig:warp_example} provides an illustration of our polynomial 
-background modeling procedure. We were able to recover 54\% of 
-Moon-contaminated data in W1 and 33\% in W2. We also apply this polynomial
-correction procedure to frames that we flagged as potentially affected
-by scattered light halos from bright solar system planets.
+background modeling procedure applied to a single L1b quadrant. We were able to 
+recover 54\% of Moon-contaminated data in W1 and 33\% in W2. We also apply this
+polynomial correction procedure to frames that we flagged as potentially 
+affected by scattered light halos from bright solar system planets.
 
@@
 
-Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
-which illustrate visually the reduction in statistical noise which has been 
+Figure \ref{fig:image_noise} shows zoom-ins of a low ecliptic latitude field,
+illustrating visually the reduction in statistical noise which has been 
 achieved by doubling the number of input exposures.
@@
            AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
-           images are rendered with identical color stretches.}
+           images are rendered with identical grayscale stretches.}
  \end{center}
@@
 were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
-providing HPC assistance. We thank many members of the DECaLS/MzLS data team for
-valuable feedback, especially Arjun Dey, Doug Finkbeiner, John Moustakas
-and Bob Blum.
+data management and HPC assistance. We thank many members of the DECaLS/MzLS 
+data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 
+Moustakas and Bob Blum.
 

### 2016-03-01 ms.tex
initial comments from Dustin

@@
 \author{Aaron M. Meisner\altaffilmark{1,2}}
-\author{Dustin Lang\altaffilmark{3}}
+\author{Dustin Lang\altaffilmark{3,4}}
 \author{David J. Schlegel\altaffilmark{2}}
@@
 University of Toronto, Toronto, ON M5S 3H4, Canada}
+\altaffiltext{4}{Department of Physics \& Astronomy, University of Waterloo,
+200 University Avenue West, Waterloo, ON, N2L 3G1, Canada}
 
@@
 spectroscopic targets, in particular for the upcoming Dark Energy Spectroscopic
-Instrument \citep[DESI,][]{desi}. Additionally, folding in two additional scans
+Instrument \citep[DESI,][]{desi}. Furthermore, folding in two additional scans
 of WISE data at each sky location allows time-dependent artifacts to be nulled,
-largely eliminating spatial nonuformities in image quality and derivative 
+largely eliminating spatial nonuniformities in image quality and derivative 
 catalogs.
@@
 programs, using an adaptation of the \cite{lang14} unWISE methodology. These 
-`full-depth' coadds are publicly available online\footnote{http://unwise.me}.
+`full-depth' coadds are publicly available online.\footnote{http://unwise.me}
 
@@
 are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
-pole singe-exposure photometry database, we were able to confirm that the 
+pole single-exposure photometry database, we were able to confirm that the 
 All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
@@
            during the AllWISE mission phase. Rejecting Moon-contaminated
-           frames as described in \ref{sec:moon} while including
+           frames as described in $\S$\ref{sec:moon} while including
            two extra visits worth of NEOWISER data has dramatically
@@
 In the \cite{lang14} unWISE processing, no steps were taken specifically
-to mitigate Moon contamination in W1 and W2. However \cite{lang14} did 
+to mitigate scattered moonlight in W1 and W2. However, that analysis did 
 address Moon contamination in W3 and W4. \cite{lang14}
@@
 frames which are contaminated by moonlight, while still retaining 
-sufficient uncontaminated coverage everywhere on the sky to avoid leaving
+sufficient artifact-free coverage everywhere on the sky to avoid leaving
 any holes in the stacks.
@@
 ranging from brown dwarf searches to IR quasar variability studies. As
-additional years worth of NEOWISER data become publicly available, it
-will be necessary to continue updating the full-depth AllWISE+NEOWISER coadds
-to maximize the achieved W1/W2 depths. Finally, the creation WISE-only (as 
+additional years of NEOWISER data become publicly available, it will be 
+necessary to continue updating the full-depth AllWISE+NEOWISER coadds to 
+maximize the achieved W1/W2 depths. Finally, the creation of WISE-only (as 
 opposed to forced photometry) catalogs based on deep coadds which incorporate
-NEOWISER images will be needed to enable a variety of exciting
-discoveries.
+NEOWISER images will be needed to enable a variety of exciting discoveries.
 
@@
 % cite software packages such as numpy, scipy, matplotlib ??
-% mention idlutils
 

### 2016-03-01 ms.tex
added DECaLS reference, clean-up of DECaLS DR1 versus DR2 explanation

@@
 
-The only existing catalogs based on our AllWISE+NEOWISER W1/W2 coadds
-are forced photometry catalogs corresponding to DECam Legacy
-Survey\footnote{http://legacysurvey.org} (DECaLS) DR2 optical sources. 
-Optical sources from DECaLS DR1 are accompanied by forced based on the
-\cite{lang14} W1/W2 coadds. Therefore, comparing the S/N of W1/W2
-fluxes in DR2 versus DR1 allows us to obtain a preliminary estimate of the 
-increased depths in regions of low ecliptic and high galactic latitude.
+The only existing catalogs based on our AllWISE+NEOWISER coadds
+are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
+\citep[DECaLS;][]{decals}, which include W1-W4 forced photometry for all
+optically detected sources. On the other hand, optical sources in DECaLS DR1
+are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
+Therefore, comparing the S/N of W1/W2 fluxes in DR2 versus DR1 can allow us to 
+obtain estimates of the depth increases for regions of low ecliptic and high 
+galactic latitude.
 

### 2016-03-01 ms.tex
no hyphen in zero point

@@
 image includes a \verb|MAGZP| header keyword which gives the nominal
-Vega zero-point of that exposure. These zero-points are essentially
+Vega zero point of that exposure. These zero points are essentially
 predictions of system throughput based on predictors such as beam splitter

### 2016-03-01 ms.tex
fill in W2 SGC figure caption

@@
            Moon-contaminated frames. It is clear that the scattered
-           moonlight has been largely removed in W2, although 
-           some traces still remain.}
+           moonlight, which appears as a series of vertical streaks, has been 
+           largely removed in W2, although some traces still remain. The
+           two dotted red boxes show locations where Jupiter passed through
+           the WISE field of view. The imprints of such planet sightings have 
+           now been removed.}
  \end{center}
@@
 find that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.
-
-% figure showing before/after of SGP on large scales in both W1/W2
 

### 2016-03-01 ms.tex
update caption of W1 SGC figure

@@
   \epsfig{file=w1_large_scale.eps, width=7.0in}
-  \caption{\label{fig:w1_large} A sub-section of the region shown in Figure
-           \ref{fig:w2_large}. Top: \cite{lang14}
+  \caption{\label{fig:w1_large} A subsection of the region displayed in Figure
+           \ref{fig:w2_large}, now shown in W1. Left: \cite{lang14}
            unWISE coadds based on the AllWISE release imaging and without
-           rejection of Moon-contaminated frames. Bottom: same region of
+           rejection of Moon-contaminated frames. Right: same region of
            sky in our new AllWISE+NEOWISER stacks, with double the
@@
            Moon-contaminated frames. Scattered moonlight has effectively
-           been completely eliminated in W1.}
+           been completely eliminated in W1. The
+           two dashed red boxes show locations where Jupiter passed through
+           the WISE field of view. The imprints of such planet sightings have 
+           now been removed}
  \end{center}

### 2016-03-02 ms.tex
another round of edits

@@
 applications, including target selection for upcoming spectroscopic cosmology 
-surveys, discovery of distant/massive galaxy clusters, and 
-identification of high-redshift quasars. In particular, our full-depth 
+surveys, identification of distant/massive galaxy clusters, and discovery
+ of high-redshift quasars. In particular, our full-depth 
 AllWISE+NEOWISER coadds will be an important input for the Dark Energy 
@@
 
-More specifically, WISE launched in December 2009, and undertook a seven 
+WISE launched in December 2009, and undertook a seven 
 month, full-sky survey in all of W1-W4 from February 2010 through August
@@
 recommenced surveying the sky in W1 and W2. This W1/W2 survey is referred to as 
-NEOWISE-Reactivation (NEOWISER) and is expected to continue until 2017.
-Importantly, the NEOWISER data are of very nearly the same high quality as
-pre-hibernation W1/W2 WISE imaging \citep{neowiser}.
+NEOWISE-Reactivation (NEOWISER) and is expected to continue until 2017. The
+first-year NEOWISER data products, including all single-exposure images,
+were publicly released in March 2015. Importantly, the NEOWISER images are of 
+very nearly the same high quality as those of the pre-hibernation WISE mission
+\citep{neowiser}.
 
@@
 However, until now, no full-sky set of W1/W2 coadds combining all pre and post 
-reactivation exposures has existed. The primary motivation for such a data 
-product is the enhanced infrared depths achieved, which, among
-other benefits, will improve the utility of WISE in selecting higher-redshift 
-spectroscopic targets, in particular for the upcoming Dark Energy Spectroscopic
-Instrument \citep[DESI,][]{desi}. Furthermore, folding in two additional scans
-of WISE data at each sky location allows time-dependent artifacts to be nulled,
-largely eliminating spatial nonuniformities in image quality and derivative 
-catalogs.
+reactivation exposures has existed. The primary motivation for such a
+data product is the enhanced depth achieved relative to AllWISE-only coadds. 
+Among other benefits, this added depth will improve the utility of WISE for 
+selecting higher-redshift spectroscopic targets, in particular for the upcoming
+Dark Energy Spectroscopic Instrument \citep[DESI,][]{desi}. Furthermore, 
+folding in two additional scans of WISE data at each sky location allows
+time-dependent artifacts to be nulled, largely eliminating spatial 
+nonuniformities in image quality and derivative catalogs.
 
@@
 important aspects of the unWISE coaddition framework we employ and list the 
-processing steps which are newly introduced in this work. In 
-$\S$\ref{sec:calib} we describe an empirical, custom photometric calibration we
+processing features which are newly introduced in this work. In 
+$\S$\ref{sec:calib} we describe an empirical photometric calibration we
 derived in order to combine pre and post reactivation WISE images. In 
 $\S$\ref{sec:moon} we describe our rejection of time-dependent artifacts, 
-particularly off-axis Moon contamination. In $\S$\ref{sec:recover} we describe
+particularly scattered moonlight. In $\S$\ref{sec:recover} we describe
 our procedure for recovering Moon-contaminated exposures. In 
@@
 have resulted from doubling the amount of W1/W2 imaging. We conclude in 
-$\S$\ref{sec:future} with a brief discussion of future uses of our present 
-AllWISE+NEOWISER coadds, as well as remaining work to be done with existing and 
-future NEOWISER imaging.
+$\S$\ref{sec:future} with a brief discussion of the work which still remains to
+be done with existing and future NEOWISER imaging.
 
@@
 
-The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
+The WISE single-exposure ``L1b'' images represent
 the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
@@
 bitmask values and uncertainty estimates. We have obtained a local copy of 
-these files for every publicly available W1 and W2 frameset, including those 
+these files for every publicly available frameset, including those 
 from the AllWISE release ($\sim$2.8M framesets) and first-year NEOWISER release
@@
 Like the official WISE Atlas coadds, unWISE processing divides the sky
-into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
+into a set of 18240 1.56$^{\circ}$$\times$1.56$^{\circ}$ tiles
 arranged along iso-declination rings. Whereas the Atlas images
@@
 relative to zero point variations measured empirically with single-exposure
-photometry of calibrator sources \citep{cutri13, cutri15}.
+photometry of calibrator sources \citep[e.g.][$\S$V.3.a.iii.1]{cutri13}.
 
@@
 wedge defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ near the south ecliptic
-pole to exclude the LMC. The positions and nominal average magnitudes of our 
+pole to exclude the LMC. The positions and average magnitudes of our 
 moderately bright source sample were drawn from the AllWISE Source Catalog, 
-selecting sources with 10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ 
-\verb|w2mpro| $<$ 11.7 and with \verb|w?cc_map|=0 in the band of interest.
+selecting W1 sources with 10.6 $<$ \verb|w1mpro| $<$ 13.1 and W2 sources
+with 9.2 $<$ \verb|w2mpro| $<$ 11.7, always requiring \verb|w?cc_map|=0 in the 
+band of interest.
 
@@
 
+% consider dropping last sentence ?
+
 \begin{figure*} [ht]
@@
            of stars near the ecliptic poles, as described in 
-           $\S$\ref{sec:calib}. The black lines show the
+           $\S$\ref{sec:calib}. The gray lines show the
            \texttt{MAGZP} zero point values provided by the L1b header 
@@
 median All-Sky phase flux. We then grouped these 
-multiplicative enhancement factors into one-day bins, and quote the median per 
+flux enhancement factors into one-day bins, and quote the median per 
 bin as the change in multiplicative
@@
 The WISE scan strategy is such that a typical sky location will be 
-observed at approximately six month intervals, with each six monthly
-``visit'' yielding a series of $\sim$12 exposures within a time span of $\sim$1
-day. During the AllWISE release, most of the sky experienced just two visits
+observed at approximately six month intervals, with each six-monthly
+``visit'' yielding a series of $\sim$12 exposures over a $\sim$1
+day time span. Within the AllWISE release, most of the sky contains just two 
+visits
 of W1/W2 imaging. Incorporating exposures from both the AllWISE and
@@
 concern for time dependent artifacts, we would risk corrupting regions of the 
-sky that were pristine during the AllWISE phase. We have found that by 
+sky that were pristine during the AllWISE phase. Instead, we have found that by 
 leveraging the added redundancy of extra NEOWISER visits while carefully 
@@
   \caption{\label{fig:moon_3433p000} Tile 3433p000, a 
-           1.5$^{\circ}$$\times$1.5$^{\circ}$ region of sky at low
+           1.56$^{\circ}$$\times$1.56$^{\circ}$ region of sky at low
            ecliptic latitude which experienced strong Moon contamination 
@@
            \cite{lang14} version of this tile. For this tile, we were
-           able to recover 58\% (18\%) of frames in W1 (W2).}
+           able to recover 58\% (18\%) of Moon-contaminated frames in W1 (W2).}
  \end{center}
@@
 discarded those frames with abnormally large pixel value standard deviations,
-indicative of a strongly varying background level (see \cite{lang14} $\S$2
+indicative of a strongly varying background level (see \citealt{lang14} $\S$2
 for full details). In the present work we have applied this same
@@
 occurrences. In constructing our new full-depth coadds, we have used the Known 
-Solar System Possible Association list to identify all exposures in which
+Solar System Possible Association List to identify all exposures in which
 Mars, Jupiter or Saturn fall within the WISE field of view. We discard
@@
            $\S$\ref{sec:recover}. Shown here is quadrant 2
-           of W1 exposure 05245b140. This quadrant was successfully recovered.}
+           of W1 exposure 05245b140. This quadrant was successfully recovered.
+           The polynomial background correction is subtracted
+           from every pixel in the L1b quadrant, but is shown masked
+           for the sake of visual comparison to the masked L1b quadrant.}
 % mention which tile used as reference?
@@
 rather than simply discard it all outright. To that end, we have added an 
-after-burner step to our coaddition procedure which attempts to salvage those 
-frames which were flagged with \verb|MOON_MASKED| and displayed abnormally 
-large pixel value standard deviations. The procedure we employ is a variant of 
-that described in $\S6.4.1$ of \cite{meisner14}.
+after-burner step to our coaddition procedure, during which we attempt to 
+salvage frames that were flagged with \verb|MOON_MASKED| and displayed 
+abnormally large pixel value standard deviations. The procedure we employ is a 
+variant of that described in $\S6.4.1$ of \cite{meisner14}.
 
@@
 evaluate the chi-squared of this model, using the reference coadd's per-pixel
-standard deviation to construct per-pixel uncertainty estimates.
+standard deviation values to construct per-pixel uncertainty estimates.
 
@@
 Figures \ref{fig:w2_large} and \ref{fig:w1_large} show large-scale renderings 
-of our full-depth coadds over the north and south Galactic caps respectively. 
-It is apparent that the Moon contamination has been completely eliminated in
+of our full-depth coadds over portions of south Galactic cap. It is apparent 
+that the Moon contamination has been completely eliminated in
 W1 and dramatically reduced in W2. It is possible that simply folding in 
@@
   \epsfig{file=w1_image_noise.eps, width=6.0in}
-  \caption{\label{fig:image_noise} Example of reduced image noise
+  \caption{\label{fig:image_noise} Example of decreased image noise
            in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
@@
 are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
-\citep[DECaLS;][]{decals}, which include W1-W4 forced photometry for all
+\citep[DECaLS,][]{decals}, which include W1-W4 forced photometry for all
 optically detected sources. On the other hand, optical sources in DECaLS DR1

### 2016-03-02 ms.tex
remove outdated comments to self, minor change to photometric calibration figure caption

@@
 
-% would be fun to say how many pixels of input there are total
-
 In addition to L1b images, we also make use of several catalog-level WISE
@@
 
-% should this section go before the ``data'' section ??
-
 To stack the W1/W2 single exposures, we make use of the \cite{lang14}
@@
 
-% mention that we use the same tile centers as Atlas and original unWISE
 Like the official WISE Atlas coadds, unWISE processing divides the sky
@@
 
-% ^ list exact exp. supp. section that discusses this
-
 We therefore sought to derive an empirical relative photometric calibration
@@
   \epsfig{file=zp_by_day.eps, width=7.0in}
-  \caption{\label{fig:zp} In each panel, the red dashes give the per-day
+  \caption{\label{fig:zp} Summary of our custom photometric calibration. In 
+           each panel, the red dashes give the per-day
            photometric zero points we derived based on repeat measurements
@@
 
-% caption of zero point figure needs to clarify the '4band', '3band', '2band' ..
-% terminology
-
 \section{Removing Time-dependent Artifacts}
@@
 
-%discuss moon first and focus on moon
 The WISE scan strategy is such that a typical sky location will be 
@@
 \end{figure*}
-% should state approximate bounding coords in terms of lambda, beta
 
@@
 data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 
-Moustakas and Bob Blum.
+Moustakas, Bob Blum and Peter Eisenhardt.
 
@@
 
-% cite software packages such as numpy, scipy, matplotlib ??
-
 \end{document}

### 2016-03-03 ms.tex
rewrite of DECaLS catalog section

@@
 $\S$\ref{sec:results} we highlight some important aspects of the full-sky set 
-of full-depth coadds generated by our processing. In $\S$\ref{sec:depth}, we 
-present a preliminary investigation of the improvements in WISE depth which 
-have resulted from doubling the amount of W1/W2 imaging. We conclude in 
+of full-depth coadds generated by our processing. In $\S$\ref{sec:depth} we 
+present a catalog-level validation of the improvements in WISE depth
+that result from doubling the amount of W1/W2 imaging. We conclude in 
 $\S$\ref{sec:future} with a brief discussion of the work which still remains to
@@
            from every pixel in the L1b quadrant, but is shown masked
-           for the sake of visual comparison to the masked L1b quadrant.}
+           for the sake of comparison to the masked L1b quadrant.}
 % mention which tile used as reference?
@@
 
-\section{Preliminary Depth Characterization}
+\section{Catalog-level Validation}
 \label{sec:depth}
@@
 relative to those based on the AllWISE-only coadds of \cite{lang14}. A
-full characterization should systematically explore a range of 
+complete characterization should systematically explore a range of 
 ecliptic and galactic latitudes, to consider the full spectrum of interplay
@@
 are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
-Therefore, comparing the S/N of W1/W2 fluxes in DR2 versus DR1 can allow us to 
-obtain estimates of the depth increases for regions of low ecliptic and high 
-galactic latitude.
+Therefore, comparing the uncertainties on W1/W2 fluxes in DR2 versus DR1 can 
+allow us to obtain estimates of the forced-photometry depth increases for 
+regions of low ecliptic and high galactic latitude.
 
-We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
-faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
-in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
-higher S/N in W1 (W2). For comparison, the expectation based purely on
-reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
-S/N.
+%We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
+%faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
+%in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
+%higher S/N in W1 (W2). For comparison, the expectation based purely on
+%reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
+%S/N.
+
+To make such a comparison, for each of W1 and W2, we select a sample of DECaLS 
+DR2 sources with \verb|type|='PSF', \verb|wise_fracflux|$<$0.1, more than
+one DECam observation, and WISE S/N within the range 10$\pm$1. We
+then obtain a DR1-DR2 comparison sample by cross-matching these DR2 objects
+with DR1 \verb|type|='PSF' sources, using a 1$''$ matching radius. The resulting
+comparison samples have $\sim$415,000 objects. For such
+sources, we find median reductions in WISE forced photometry uncertainties
+of 1.38$\times$ (1.30$\times$) in W1 (W2). The corresponding median increase in
+coverage is 1.9$\times$ in both bands, leading us to expect a factor of 
+1.38$\times$ decrease in uncertainties based purely on reduced statistical 
+noise.
+
+These values are not intended to represent the enhanced
+depths that would result from comparing WISE-only catalogs which begin with
+a source detection step on the WISE coadds. Since the DR2 forced photometry 
+does not attempt to account for faint, infrared-only sources which are
+newly revealed in the AllWISE+NEOWISER stacks, the photometric uncertainty
+reduction factors we have derived serve mostly as quantitative confirmation 
+of the decreased statistical noise shown in Figure \ref{fig:image_noise}.
 
 Much more work is needed to characterize the increased sensitivity
-of WISE to faint sources due to the inclusion of NEOWISER
+of WISE to faint infrared-only sources due to the inclusion of NEOWISER
 imaging, as this will inform forecasts about the final 3.4$\mu$m and 

### 2016-03-03 ms.tex
very minor edits

@@
 
-%We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
-%faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
-%in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
-%higher S/N in W1 (W2). For comparison, the expectation based purely on
-%reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
-%S/N.
-
-To make such a comparison, for each of W1 and W2, we select a sample of DECaLS 
-DR2 sources with \verb|type|='PSF', \verb|wise_fracflux|$<$0.1, more than
-one DECam observation, and WISE S/N within the range 10$\pm$1. We
+To make such a comparison, for each of W1 and W2, we select a sample of 
+isolated DECaLS DR2 sources with \verb|type|=`PSF', \verb|wise_fracflux|$<$0.1,
+more than one DECam observation, and WISE S/N within the range 10$\pm$1. We
 then obtain a DR1-DR2 comparison sample by cross-matching these DR2 objects
-with DR1 \verb|type|='PSF' sources, using a 1$''$ matching radius. The resulting
+with DR1 \verb|type|=`PSF' sources, using a 1$''$ matching radius. The resulting
 comparison samples have $\sim$415,000 objects. For such

### 2016-03-03 ms.tex
minor edits

@@
 poles. In contrast, the \cite{lang14} unWISE processing adopted zero points 
-based on the L1b header metadata.
+extracted from the L1b header metadata.
 \item We explicitly reject exposures contaminated by the Moon and/or solar 
@@
 complete characterization should systematically explore a range of 
-ecliptic and galactic latitudes, to consider the full spectrum of interplay
+ecliptic and Galactic latitudes, to consider the full spectrum of interplay
 between decreased statistical noise and confusion. For isolated sources in the 
@@
 allow us to obtain estimates of the forced-photometry depth increases for 
-regions of low ecliptic and high galactic latitude.
+regions of low ecliptic and high Galactic latitude.
 

### 2016-03-03 ms.tex
more minor edits

@@
 comparison samples have $\sim$415,000 objects. For such
-sources, we find median reductions in WISE forced photometry uncertainties
+sources, we find median reductions in forced photometry flux uncertainties
 of 1.38$\times$ (1.30$\times$) in W1 (W2). The corresponding median increase in
 coverage is 1.9$\times$ in both bands, leading us to expect a factor of 
-1.38$\times$ decrease in uncertainties based purely on reduced statistical 
+1.38$\times$ decrease in flux uncertainties based purely on reduced statistical 
 noise.

### 2016-03-04 ms.tex
add full DESI funding acknowledgment

@@
 
-This research used resources of the National Energy Research Scientific 
-Computing Center, a DOE Office of Science User Facility supported by the Office
-of Science of the U.S. Department of Energy under Contract No. 
-DE-AC02-05CH11231.
+This research is supported by the Director, Office of Science, Office of High 
+Energy Physics of the U.S. Department of Energy under Contract No. 
+DE–AC02–05CH1123, and by the National Energy Research Scientific Computing 
+Center, a DOE Office of Science User Facility under the same contract; 
+additional support for DESI is provided by the U.S. National Science
+Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
+the National Optical Astronomy Observatory; the Science and Technologies 
+Facilities Council of the United Kingdom; the Gordon and Betty Moore 
+Foundation; the Heising-Simons Foundation; and by the DESI Member Institutions.
 
 This research made use of the NASA Astrophysics Data System (ADS) and the IDL 
-Astronomy User's Library at Goddard. \footnote{Available at 
+Astronomy User's Library at Goddard.\footnote{Available at 
 \texttt{http://idlastro.gsfc.nasa.gov}}

### 2016-03-08 ms.tex
add Dunlap acknowledgment

@@
 Like the official WISE Atlas coadds, unWISE processing divides the sky
-into a set of 18240 1.56$^{\circ}$$\times$1.56$^{\circ}$ tiles
+into a set of 18,240 1.56$^{\circ}$$\times$1.56$^{\circ}$ tiles
 arranged along iso-declination rings. Whereas the Atlas images
@@
 Foundation; the Heising-Simons Foundation; and by the DESI Member Institutions.
+The Dunlap Institute is funded through an endowment established by the David 
+Dunlap family and the University of Toronto.
 

### 2016-03-08 ms.tex
correction from Roc: NEOWISE-Reactivation is a separate project from WISE mission

@@
 \begin{abstract} 
-Thanks to the Wide-field Infrared Survey Explorer (WISE) mission's
-NEOWISE-Reactivation (NEOWISER) program, an entire year of post-reactivation W1
-and W2 exposures were made publicly available in 2015. This data set consists of
-$\sim$2.5 million exposures in each band, effectively doubling the amount
-of WISE imaging available at 3.4$\mu$m and 4.6$\mu$m relative to the AllWISE
-release. We have created the first ever full-sky set of coadds combining all 
-publicly available W1 and W2 exposures from both the AllWISE and 
-NEOWISER mission phases. We employ an adaptation of the unWISE image coaddition
-framework \citep{lang14}, which preserves the native WISE angular resolution 
-and is optimized for forced photometry. By incorporating two additional scans
-of the entire sky, we not only improve the W1/W2 depths, but also largely
-eliminate time-dependent artifacts such as off-axis moonlight contamination.
-We anticipate that our new coadds will have a broad range of 
-applications, including target selection for upcoming spectroscopic cosmology 
-surveys, identification of distant/massive galaxy clusters, and discovery
- of high-redshift quasars. In particular, our full-depth 
-AllWISE+NEOWISER coadds will be an important input for the Dark Energy 
-Spectroscopic Instrument (DESI) selection of luminous red galaxy and quasar 
-targets. Our full-depth W1/W2 coadds are already in use within the 
+The Near Earth Object Wide-field Infrared Survey Explorer (NEOWISE)
+Reactivation mission released data from its first full year of observations
+in 2015. This data set includes $\sim$2.5 million exposures in each of W1 and
+W2, effectively doubling the amount of WISE imaging available at 3.4$\mu$m and 
+4.6$\mu$m relative to the AllWISE release. We have created the first ever 
+full-sky set of coadds combining all publicly available W1 and W2 exposures 
+from both the AllWISE and NEOWISE-Reactivation (NEOWISER) mission phases. We 
+employ an adaptation of the unWISE image coaddition framework \citep{lang14}, 
+which preserves the native WISE angular resolution and is optimized for forced 
+photometry. By incorporating two additional scans of the entire sky, we not 
+only improve the W1/W2 depths, but also largely eliminate time-dependent 
+artifacts such as off-axis scattered moonlight. We anticipate that our new 
+coadds will have a broad range of applications, including target selection for 
+upcoming spectroscopic cosmology surveys, identification of distant/massive 
+galaxy clusters, and discovery of high-redshift quasars. In particular, our 
+full-depth AllWISE+NEOWISER coadds will be an important input for the Dark 
+Energy Spectroscopic Instrument (DESI) selection of luminous red galaxy and 
+quasar targets. Our full-depth W1/W2 coadds are already in use within the 
 DECam Legacy Survey (DECaLS) and Mayall z-band Legacy Survey (MzLS) reduction 

### 2016-03-10 ms.tex
infrared

@@
 time baseline would enable a wealth of important time-domain projects,
-ranging from brown dwarf searches to IR quasar variability studies. As
+ranging from brown dwarf searches to infrared quasar variability studies. As
 additional years of NEOWISER data become publicly available, it will be 

### 2016-03-15 ms.tex
last round of edits

@@
 pipelines. Much more work still remains in order to fully leverage NEOWISER 
-imaging for astrophysical applications beyond the solar system.
+imaging for astrophysical applications beyond the inner solar system.
 \end{abstract}
 
-\keywords{methods: data analysis -- surveys -- techniques: image processing}
+\keywords{methods: data analysis -- surveys: cosmology -- techniques: image processing}
 
@@
 polynomial correction procedure to frames that we flagged as potentially 
-affected by scattered light halos from bright solar system planets.
+affected by scattered light halos from bright solar system planets. We
+categorically exclude \verb|qual_frame|=0 exposures, making no attempt to 
+recover such frames.
 
@@
            redundancy in sky coverage and rejection/recovery of 
-           Moon-contaminated frames. Scattered moonlight has effectively
-           been completely eliminated in W1. The
+           Moon-contaminated frames. Scattered moonlight (vertical streaks
+           in left panel) has been completely eliminated in W1. The
            two dashed red boxes show locations where Jupiter passed through
@@
 \acknowledgments{
-We thank Roc Cutri for his guidance in making use of the WISE data products. 
-We thank Stephen Bailey for downloading the L1b images to NERSC. We thank
-Doug Finkbeiner for providing access to the big-memory computers which
+We thank Roc Cutri for his guidance in making use of the WISE/NEOWISE data 
+products. We thank Stephen Bailey for downloading the L1b images to NERSC. We 
+thank Doug Finkbeiner for providing access to the big-memory computers which
 were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
-data management and HPC assistance. We thank many members of the DECaLS/MzLS 
+data management and HPC assistance. We thank Ben Weaver, Debbie Bard and Rollin
+Thomas for additional HPC advice. We thank many members of the DECaLS/MzLS 
 data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 

### 2016-03-22 ms.tex
minor edit
right timeline for WISE mission phases

@@
 pipelines. Much more work still remains in order to fully leverage NEOWISER 
-imaging for astrophysical applications beyond the inner solar system.
+imaging for astrophysical applications beyond the solar system.
 \end{abstract}
@@
 WISE launched in December 2009, and undertook a seven 
-month, full-sky survey in all of W1-W4 from February 2010 through August
-2010. In September 2010, the solid hydrogen cryogen used to cool the W3 and W4 
-instrumentation was depleted, significantly reducing the quality of W3 
-imaging and rendering W4 unusable. Nevertheless, WISE continued surveying 
-the sky from September 2010 to February 2011 in W1 and W2, including 
-a portion of the mission referred to as NEOWISE \citep{neowise}. In February 
-2011 WISE was placed in hibernation. In October 2013, WISE was reactivated, and
-recommenced surveying the sky in W1 and W2. This W1/W2 survey is referred to as 
-NEOWISE-Reactivation (NEOWISER) and is expected to continue until 2017. The
-first-year NEOWISER data products, including all single-exposure images,
-were publicly released in March 2015. Importantly, the NEOWISER images are of 
-very nearly the same high quality as those of the pre-hibernation WISE mission
-\citep{neowiser}.
+month, full-sky survey in all of W1-W4 from early January 2010 until 
+early August 2010. Due to the depletion of cryogen, W4 and W3 became unusable 
+in early August 2010 and late September 2010, respectively. Nevertheless, WISE 
+continued surveying the sky through January 2011 in W1 and W2, 
+including a portion of the mission referred to as NEOWISE \citep{neowise}. In 
+February 2011 WISE was placed in hibernation. In October 2013, WISE was 
+reactivated, and recommenced surveying the sky in W1 and W2. This W1/W2 survey 
+is referred to as NEOWISE-Reactivation (NEOWISER) and is expected to continue 
+until 2017. The first-year NEOWISER data products, including all 
+single-exposure images, were publicly released in March 2015. Importantly, the 
+NEOWISER images are of very nearly the same high quality as those of the 
+pre-hibernation WISE mission \citep{neowiser}.
 
